\bfseries Don't interpolate your data!

### 2022-10-22 main.tex
Figures! They need captions

@@

@@

\paragraph{Fake data}
We demonstrate the effectiveness of the spectral combination method on artificial data.
The spectral data were generated from a mean spectral expectation that is a continuum plus a randomly generated (not at all physical) line list, where each line equivalent width was set by a random draw from a power law.
Each spectral epoch was given a velocity (Doppler shift) by putting the epochs equally spaced on a sinusoidal variation with a semi-amplitude of $30\,\kmps$ (to emulate the motion of the spectrograph with respect to the Solar System barycenter).
The data were generated with an assumption of unresolved spectral lines and a Gaussian line-spread function (LSF) by simply evaluating the spectral expectation model at pixel centers, so the LSF is effectively the pixel-convolved LSF.
The individual pixel grids $x_i$ were set to slightly under-sample the pixel-convolved LSF, and they were fixed in the rest frame of the spectrograph.
After sampling the mean spectral expectation model at the pixels, we add Gaussian noise with a uniform variance such that the signal-to-noise in the continuum is XXXX per pixel in each epoch spectrum.
At a rate of XXX pixels were randomly and independently marked as ``bad'' and offset by a large offset.
At each epoch $i$, there is a spectrum $y_i$ with $M_i=XXX$ pixels, a spectrograph rest-frame pixel grid $x_i$ (in log wavelength $x$), and a $M_i$-pixel binary bad-pixel mask $b_i$.
The full data set is shown in Figure~\label{fig:data}, and a zoom-in on one epoch is shown in \figurename~\ref{fig:datazoom}.

@@

We show the results of Standard Practice (tm), for the fake data, in \figurename~\ref{fig:standard}.
We also show the comparison with the true spectral expectation model that was employed to make the fake data.
We find HOGG WHAT??

@@

The combined spectrum resulting from the Forward Model (tm) described in \sectionname~\ref{sec:method} is shown in \figurename~\ref{fig:combined}.
Again, it is compared to the true spectral expectation model.
We find HOGG WHAT?? HERE SAY ABSOLUTELY WHAT WE FIND.

@@

\paragraph{Dependence on raw-data pixel scale}
HOGG show that things with Standard Practice (tm) depend VERY STRONGLY on the input pixel grid.

@@

Plot the empirical covariances as a function of input-data pixel scale, interpolation method, and number of epochs.

>>>>

% Copyright 2022 David W. Hogg (NYU) and Andy Casey (Monash)

% To-Do items
% -----------
% - Audit and fix the sign applied to $\Delta x_i$ everywhere. Wrong relative to code?
% - Write about the two input-data cases.
% - See bug list in code for other issues with the text--code relationship (noise model; line-formation model).
% - Copy in a figure macro from Hogg & Villar and use it.

@@

% figure setup
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{shadows}
\definecolor{captiongray}{HTML}{555555}
\mdfsetup{%
  innertopmargin=2ex,
  innerbottommargin=1.8ex,
  linecolor=captiongray,
  linewidth=0.5pt,
  roundcorner=1pt,
  shadow=false,
}
\newlength{\figurewidth}
\setlength{\figurewidth}{0.75\textwidth}

@@

\paragraph{Fake data}
We demonstrate the effectiveness of the spectral combination method on artificial data.
The spectral data were generated from a mean spectral expectation that is a continuum plus a randomly generated (not at all physical) line list, where each line equivalent width was set by a random draw from a power law.
Each spectral epoch was given a velocity (Doppler shift) by putting the epochs equally spaced on a sinusoidal variation with a semi-amplitude of $30\,\kmps$ (to emulate the motion of the spectrograph with respect to the Solar System barycenter).
The data were generated with an assumption of unresolved spectral lines and a Gaussian line-spread function (LSF) by simply evaluating the spectral expectation model at pixel centers, so the LSF is effectively the pixel-convolved LSF.
The individual pixel grids $x_i$ were set to slightly under-sample the pixel-convolved LSF, and they were fixed in the rest frame of the spectrograph.
After sampling the mean spectral expectation model at the pixels, we add Gaussian noise with a uniform variance such that the signal-to-noise in the continuum is XXXX per pixel in each epoch spectrum.
At a rate of XXX pixels were randomly and independently marked as ``bad'' and offset by a large offset.
At each epoch $i$, there is a spectrum $y_i$ with $M_i=XXX$ pixels, a spectrograph rest-frame pixel grid $x_i$ (in log wavelength $x$), and a $M_i$-pixel binary bad-pixel mask $b_i$.
The full data set is shown in Figure~\label{fig:data1}, and a zoom-in on one epoch is shown in \figurename~\ref{fig:data2}.
\begin{figure}[t!]
    \begin{mdframed}\begin{center}
    \includegraphics[width=1.3\figurewidth]{notebooks/data1.pdf}\\
    \includegraphics[width=\figurewidth]{notebooks/datazoom.pdf}
    \end{center}
    \caption{HOGG: Something.}
    \label{fig:data1}
    \end{mdframed}
\end{figure}
\begin{figure}[t!]
    \begin{mdframed}\begin{center}
    \includegraphics[width=1.3\figurewidth]{notebooks/data2.pdf}
    \end{center}
    \caption{HOGG: Something.}
    \label{fig:data2}
    \end{mdframed}
\end{figure}

@@

We show the results of Standard Practice (tm), for the fake data, in \figurename~\ref{fig:standard}.
We also show the comparison with the true spectral expectation model that was employed to make the fake data.
We find HOGG WHAT??
\begin{figure}[t!]
    \begin{mdframed}\begin{center}
    \includegraphics[width=\figurewidth]{notebooks/standard1.pdf}\\
    \includegraphics[width=\figurewidth]{notebooks/standard2.pdf}
    \end{center}
    \caption{HOGG: Something.}
    \label{fig:standard}
    \end{mdframed}
\end{figure}

@@

The combined spectrum resulting from the Forward Model (tm) described in \sectionname~\ref{sec:method} is shown in \figurename~\ref{fig:forward}.
Again, it is compared to the true spectral expectation model.
We find HOGG WHAT?? HERE SAY ABSOLUTELY WHAT WE FIND.
\begin{figure}[t!]
    \begin{mdframed}\begin{center}
    \includegraphics[width=\figurewidth]{notebooks/forward1.pdf}\\
    \includegraphics[width=\figurewidth]{notebooks/forward2.pdf}
    \end{center}
    \caption{HOGG: Something.}
    \label{fig:forward}
    \end{mdframed}
\end{figure}

@@

@@

Plot the empirical covariances as a function of input-data pixel scale, interpolation method, and number of epochs.
\begin{figure}[t!]
    \begin{mdframed}\begin{center}
    \includegraphics[width=\figurewidth]{notebooks/noise.pdf}
    \end{center}
    \caption{HOGG: Something.}
    \label{fig:noise}
    \end{mdframed}
\end{figure}
